Paper Two

### 2023-02-24 Paper Two .qmd
add introducation and research interests

@@

>>>>

Air pollution is a significant contributor to the development of disease and premature death, and is widely recognized as the largest environmental risk factor to human health globally (WHO, 2016). (\@https://www.who.int/phe/publications/air-pollution-global-assessment/en/) Exposure to air pollution increases the risk of premature mortality from heart disease, stroke, and lung cancer. Advances in health and atmospheric sciences have made it possible to estimate the number of deaths and illnesses associated with air pollution, using information from peer-reviewed scientific literature. The relationship between population-level pollution exposure, both short-term and long-term, and adverse health outcomes, including premature death and hospital visits, is expressed through the concentration-response function. Cohen et al. (\@https://pubmed.ncbi.nlm.nih.gov/28408086/), the Institute for Health Metrics and Evaluation and the Health Effects Institute, and the World Health Organization have developed estimates of air pollution-attributable deaths and other adverse health outcomes globally and for individual countries. (\@https://www.who.int/phe/publications/air-pollution-global-assessment/en/)

Globally, air pollution was responsible for 8.7% of deaths in 2017, making it the fifth leading mortality risk, with 4.9 million premature deaths worldwide. Canada is among the top 10 countries with the lowest national PM2.5 exposure levels, according to analyses. (\@https://www.stateofglobalair.org/)  In Canada, air pollution ranks as the 11th largest risk factor overall for premature death and disability, and is the top environmental risk. (\@https://www.canada.ca/en/health-canada/services/publications/healthy-living/2021-health-effects-indoor-air-pollution.html)

Therefore, it is crucial to reduce air pollution by introducing a stainable policy and method. According to LI and YIN (@\https://www.sciencedirect.com/science/article/abs/pii/S1570667211601906) and  Topalovic et al. (\@https://www.sciencedirect.com/science/article/pii/S0959652620341949#bbib50), subways are the most effective mode of transportation for reducing congestion and greenhouse emissions due to their speed, efficiency, safety, and environmental benefits. Furthermore, as noted by Chen and Whalley (@https://www.sciencedirect.com/science/article/pii/S0959652620341949#bbib10) and Gendron-Carrier et al. (\@https://www.sciencedirect.com/science/article/pii/S0959652620341949#bbib19), the operation of subways can lead to improvements in air quality, reduced mortality rates resulting from air pollution, increased productivity, and reduced social costs.

@@

There is also study which conducted in China. The results of the study matchs with our findings. It further suggests two policy recommendations. Firstly, the government should actively promote green transportation as an alternative to motor vehicles. This can be achieved by increasing the availability of green vehicles and reducing the number of public motor vehicles to reduce emissions. Secondly, the development of subway systems should be rationally planned to minimize the negative impact on urban air pollution, particularly PM2.5. The government can increase the accessibility of subways by developing a complex subway network, which can help meet residents' travel demands and reduce emissions. However, expanding existing subway lines may not be enough to change people's travel mode, so it may be more effective to increase the number of subway lines. Since subway projects are expensive, a rational plan for the subway network can help achieve the goal of reducing air pollution while also considering the fiscal investment required. (\@https://www.sciencedirect.com/science/article/pii/S0959652620341949)
